---
title: "P8105_hw6_yj2752"
author: "Yixuan Jiao"
output: html_document
---

## Import packages

```{r}
library(tidyverse)
library(purrr)
library(modelr)
```

## Problem2
First, cleaning the dataset. Certain cities have been excluded, only white and black are kept for race analysis. Unknown sex are dropped.
```{r}
homicide <- 
  read_csv("./data/homicide-data.csv") %>%
  mutate(city_state = str_c(city,",",state),
         victim_age = as.numeric(victim_age),
         resolved_binary = if_else(disposition == "Closed by arrest", 1, 0)) %>%
  filter(! city_state %in% c("Dallas,TX" ,"Phoenix,AZ","Kansas City,MO","Tulsa,AL")) %>%
  filter(victim_race %in% c("White","Black")) %>%
  filter(victim_sex %in% c("Male","Female")) %>%
  select(city_state,resolved_binary,victim_age,victim_race,victim_sex)
```
Fitting the linear model for Baltimore, MD with resolved status as outcome and age, sex, race as predictors.
```{r}
fit_logistic_homicide = 
  homicide %>% 
  filter(city_state == "Baltimore,MD") %>%
  glm(resolved_binary ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 
```
The model shows that the odds ratio for solving homicides comparing male victims to female victims is 0.426 with confidence interval (0.325,0.558). 
```{r}
fit_logistic_homicide %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         CI_lower = exp(estimate - 1.96*std.error),
         CI_upper = exp(estimate + 1.96*std.error)) %>%
  select(term, log_OR = estimate, OR, CI_lower, CI_upper, p.value) %>% 
  knitr::kable(digits = 3)
```
Same procedure is applied to each city in the dataset. Data from each city will generate a unique model storing the column linear model. Tidy and unnest the column and only keep the vicitim_sexMale term to make the plot.
```{r}
homicide <- 
  homicide %>%
  nest(data = -city_state) %>%
  mutate(linear_model = map(.x = data, ~glm(resolved_binary ~ victim_age + victim_race + victim_sex, data = .x, family =  binomial()) %>% broom::tidy())) %>%
  unnest(linear_model) %>%
  mutate(OR = exp(estimate),
         CI_lower = exp(estimate - 1.96*std.error),
         CI_upper = exp(estimate + 1.96*std.error)) %>%
  select(city_state,term, log_OR = estimate, OR, CI_lower, CI_upper, p.value) %>%
  filter(term == "victim_sexMale")

head(homicide) %>% knitr::kable(digits = 3)
```
The plots shows the odds ratio of each cities with CI as error bar. Most cities (except Albuquerque, Stockton, Fresno, Nashville, and Richmond) have OR lower than 1, meaning that in different extent, the odds of having a male victim homicide case solved is generally lower among the female victim cases.
```{r}
homicide %>%
  mutate(city_state = fct_reorder(city_state,OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  labs(y = "Odds Ratio for Male Victim Homicide Solved",
       x = "City") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## Problem3
First, load the dataset and clean the data. The data set has no missing value. I changed babysex's number into two factors.
```{r}
baby <- 
  read_csv("data/birthweight.csv") %>%
  mutate(babysex = if_else(babysex == 1,"male","female"))
```
By searching on internet, I believe mother's and baby's physical condition is crucial to the birthweight. So I decide to build the model according to baby's physical measure and certain mother's important measures.
```{r}
lm1 <- lm(bwt ~ babysex + blength + momage + parity + delwt + ppwt, data = baby)
```
The predictions vs. residuals polot is shown below, most of the part is around 0.
```{r}
baby %>%
  add_residuals(lm1) %>%
  add_predictions(lm1) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```
The formulas for other 2 models are shown below with their summary
```{r}
lm2 <- lm(bwt ~ blength + gaweeks, data = baby)
lm3 <- lm(bwt ~ (bhead + blength + babysex)^3, data = baby)
lm2 %>% broom::tidy()
lm3 %>% broom::tidy()
```
The cross validation result shows my model is similar to the model that only contains 2 main effect. And the last model contains head circumstance, length and sex and all interactions has overall lower rmse distribution (indicating that's possibly a better model comparing the first 2). 
```{r}
crossv_mc(baby,100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>%
  mutate(
    lm1 = map(train,~lm(bwt ~ babysex + blength + momage + parity + delwt + ppwt, data = .x)),
    lm2 = map(train,~lm(bwt ~ blength + gaweeks, data = .x)),
    lm3 = map(train,~lm(bwt ~ (bhead + blength + babysex)^3, data = .x))) %>%
  mutate(
    rmse_lm1 = map2_dbl(lm1, test, ~rmse(model = .x, data = .y)),
    rmse_lm2 = map2_dbl(lm2, test, ~rmse(model = .x, data = .y)),
    rmse_lm3 = map2_dbl(lm3, test, ~rmse(model = .x, data = .y))
  ) %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

